### 2014-11-12 tex/definitions.tex
Reworked supplemental upto definitions and proofs.

\subsection{Heap Properties}

>>>>

\section{Definitions}

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

A special reference, $\cfgnt{r}_\mathit{un}$, and location,
$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
initialization. The '$\mathit{un}$' is to indicate the reference or
location is uninitialized at the point of execution.

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An
initial state is a state meeting the following conditions: The range
of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the
function R is defined only for location $l_0$, and for any field $f$,
$R(l_0,f)$ returns $r_{un}$.
\end{definition}

The rewrite rules that define the Javalite semantics are presented in
the supplemental document accompanying the paper.

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary
relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times
\mathcal{S} $, which relates machine states with successor states. Two
important state transition relations are \textbf{GSE} $\rgse$ and
\textbf{symbolic} $\rsym$. Each of these use a separate relation for
initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of
these transition relations are defined in \figref{fig:lazy},
\figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

### 2014-11-12 tex/lazy.tex
Reworked supplemental upto definitions and proofs.

Recall that in generalized symbolic execution (GSE) for lazy
initialization of symbolic references consists of three key points of
non-determinism where each symbolic reference can be initialized
non-deterministically to null, a new instance of the symbolic
reference, or aliases to symbolic references of the same type
previously initialized. The initialization in GSE consists of creating
branches in the execution tree for all the non-deterministic choices.

@@

\input{lazy-eq}

>>>>

The specialization of Javalite to generalized symbolic execution with
lazy initialization using the summary heap is in \figref{fig:lazyInit}
for the initialization and \figref{fig:lazy} for how the
initialization is used. Specifically, the field-access rule in
\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
the accessed field is instantiated. Initialization in generalized
symbolic execution never happens for more than one object on any use
of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly one
location.

An uninitialized object may be lazily initialized
non-deterministically to null, a new instance of the object, or an to
an object of the same type also initialized lazily. The
non-deterministic initialization creates branches in the execution
tree during state space exploration.

The $\rgse$ relation is a union over branching points on control flow
to support the final proof of the existence of a
bisimulation. Although it is apparent that there is non-determinism in
initialization, it is not the initialization where control flow
diverges in program execution. Rather, that occurs at branches and
exceptions, and that is reflected in the composition of $\rgse$.

@@
